SDR enhancement by clouds

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 12:14

We used as reference a modelled clear sky approximation,

@@

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

>>>>

We used as reference a modeled clear sky approximation,

@@

A secondary criteria was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane Equation \ref{eq:ECE}
